Workshop

### 2019-09-06 week4/workshop.tex
last exercise.

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage[utf8]{inputenc}
\usepackage[spanish, mexico]{babel}

\title{Taller}
\author{Miguel A. Gomez B.}

@@

\paragraph{Proof.}

@@

\newpage

@@

With $b \neq 0$. By squaring this number we obtain

@@

>>>>

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage[utf8]{inputenc}

\title{Workshop}
\author{Miguel A. Gomez B.}

@@

\paragraph{Proof.} that form comes as a representation of every natural number by its residual, in this case is $3$, we notice that every natural number can be represented on one of the following forms:

$$3n = 0, 3, 6 ,9 \dots$$
$$3n + 1 = 1, 4, 7, 10, \dots$$
$$3n + 2 = 2, 5 , 8, 11, \dots$$

$3n + 3$ is on the first category, we see that this number can be factored as $3(n+1)$.

\paragraph{} On the decomposition of $3n +2$ we can say by the Fundamental Theorem of arithmetic that $3n + 2$ could be composed by primes of the form $3n + 1$ and $3n + 2$, $3n$ is not an option becasue $3n + 2$ does not comply with the initial form. Let us asume that $3n + 2$ is composed only by primes of the form $3n +1$:

$$3n + 2 = (3k_0 + 1) (3k_1 + 1) (3k_2 + 1) \dots$$

Then,

\begin{align*}
  (3k_0 + 1)(3k_1 + 1) &= 9k_0k_1 + 3k_0 + 3k_1 + 1\\
  &= 3(3k_0k_1 + k_0 + k_1) + 1
\end{align*}

but that is a contradiction, because $3(\dots) + 1$ would never be of the form $3n + 2$. Then the only possible factor must be another $3k +2$. $\blacksquare$

@@

@@

With $b \neq 0$ and $\frac{a}{b}$ an irreducible fraction. By squaring this number we obtain

@@

\paragraph{5.} Prove that if $n>2$, then there exists a prime $p$ satisfiying $n<p<n!$.

\paragraph{Proof.} supose that we multiply each prime number such as  $p<n$, if that is the case that product must be less than $n!$. To that product, add 1:

$$n < p_1 p_2 p_3 p_n < n!$$
$$n < (p_1 p_2 p_3 p_n) + 1 < n!$$

Then this number would be a prime or would be a composite, but a new prime greater than n will be required to represent that number. We conclude that this number $p$ satisfies  $n < p < n!$. $\blacksquare$
